HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-05 LaTeX/ms.tex
Finished addressing comments.
Almost there.
Stay on target, stay on target.

The sample was selected to be a complete, flux-limited set of objects
satisfying $S_{500} > 95\,$mJy that are not known radio AGN, nearby late-type
galaxies, or Galactic emission. The selection was designed to assemble a large
sample of lensed galaxies in the ALMA-accesible HerMES fields, and was
constructed from the SUSSEXtractor catalogs, which were available prior to the
ALMA Cycle~0 deadline.  Subsequently, improved efforts to deblend SPIRE
photometry at 500$\,\mu$m using StarFinder \citep{Wang:2014lr} were introduced
that formed the basis of the lens selection criteria used in
\citet{Wardlow:2013lr}.  As a result of the improved deblending algorithms in
the StarFinder catalogues and \citet{Wardlow:2013lr} a number of objects in our
sample have significantly lower $S_{500}$ values in the StarFinder catalog than
in the original SUSSEXtractor catalogs.  This and further investigation into
the StarFinder catalogs shows that their original flux was boosted by blending
with nearby sources rather than by gravitational lensing.  For this reason, the
objects in this sample comprise a combination of lenses and blends of multiple
sources.

@@

Figure~\ref{fig:sample} shows that the {\it Herschel}-ALMA sample is set
clearly apart from the very bright {\it Herschel} DSFGs that are selected to
have $S_{500} > 100 \, $mJy and have been shown to be almost entirely lensed
DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
the sample in this paper should include a more diverse mix of lensed and
unlensed DSFGs.  On the other hand, this sample is selected from a survey with
an area that is 200 times larger than that of the Large Apex Bolometer Camera
Extended Chandra Deep Field Survey \citep[LESS][]{Weis:2009ly}.  It is no
surprise then, that the median $S_{500}$ in our sample is $\sim3.5$ times
brighter than the median $S_{500}$ in the sample of ALMA-detected sources in
LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it Herschel}-ALMA sample
opens a new window of discovery space on the bright end of the DSFG luminosity
function.

@@

Our methodology follows the procedures outlined in previous efforts to predict
magnification factors for DSFGs with a given apparent flux density
\citep[chiefly,][]{Lima:2010fk, Wardlow:2013lr}.  We summarize the essential
elements here and highlight significant differences where appropriate.
Additional details may be found in Fialkov et al. (in prep.).

@@

To describe $\rho_{\rm lens}\,(r)$, we use a superposition of a singular
isothermal sphere (SIS) and a Navarro-Frenk-White (NFW) profile
\citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
describes the outskirts of dark matter halos better, while the SIS profile is
preferred on smaller scales because it correctly fits the observed flat
rotational curves in galaxies.  We make sure that the resulting probability
density of lensing, $P\,(\mu)$, is normalized to unity.  To describe $n_{\rm
lens}\,(M, \, z)$, we generate the abundance of halos at each mass and redshift
using the \citet{Sheth:1999kx} formalism.  To describe $dN_{\rm source}/dz$, we
adopt the following redshift distribution which is based on photometric
redshifts of optical counterparts to ALMA sources identified in ALESS
\citep{Simpson:2014lr} and has been modified to a lower redshift to reflect the
relatively blue SPIRE colors of the sample:

@@

\noindent where $a_z = 1 + z$, $z_\mu = 1.5$, and $\sigma_z = 0.2$.

We explore a variety of intrinsic luminosity functions that are described by
either a single Schechter function or a broken-power law.  These luminosity
functions are selected to represent the range of observed instrinsic luminosity
functions for DSFGs, which are shown in the left panel of
Figure~\ref{fig:lensstats} and are drawn from the ALESS survey
\citep{Karim:2013lr} and from interferometric follow-up of the first AzTEC
survey in COSMOS \citep{Scott:2008qy} using the SMA \citep{Younger:2007fk,
Younger:2009lr} and PdBI \citep{Miettinen:2015lr}.  Interferometric follow-up
data in COSMOS \citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are
published, but unknown completeness corrections in the single-dish surveys on
which these follow-up datasets are based precludes their use here.

The Shechter function we adopt has the usual form \citep{Schechter:1976yq}

\begin{equation}
\frac{dn}{dS^\prime} = \frac{n_\ast}{S_\ast}
\left(\frac{S^\prime}{S_\ast}\right)^{-\alpha}
\exp\left(\frac{-S^\prime}{S_\ast}\right),
\end{equation}

\noindent while the broken power-law has the form

@@

In Table~\ref{tab:models}, we provide information for two models tested in this
paper: the \citet{Karim:2013lr} broken power-law that provides a good fit to
ALESS number counts; and a broken power-law with a brighter break point
($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
from \citet{Miettinen:2015lr}.  The interferometric observations in
\citet{Miettinen:2015lr} show that all of the sources in their survey are
either unlensed or lensed by magnification factors $<2$.  Therefore, the ALESS
and COSMOS luminosity functions bracket the plausible range of intrinsic
luminosity functions for DSFGs.  The data and corresponding luminosity
functions are shown in the left panel of Figure~\ref{fig:lensstats}.

@@

The product of the model is the lensing optical depth for a given lensing galaxy
and source galaxy. The sum over the distribution of source redshifts and lens
masses and redshifts yields the total optical depth for lensing,  $f_\mu$. The
lensing probability with magnification larger than $\mu$ is then calculated via
$P(>\mu) = 1-\exp(-f_\mu)$ and the differential probability distribution is
$P(\mu) = -dP(>\mu)/d\mu$.  The sum over the distribution of source redshifts
and lens masses and redshifts yields the total probability distribution
function.

The fundamental measurement provided by the spatially resolved SMA and ALMA
imaging and associated lens models is the magnification factor of a source with
a given apparent $S_{870}$.  Due to the large size of the combined sample, we
can compute the average magnification as a function of $S_{870}$ from the data:
$\langle\mu_{870}\rangle$.  The same quantity can also be directly computed from our
model as

@@

%The regime between the low and high apparent flux density limits ($10\,$mJy$ <
%S_{870} < 70\,$mJy) is where the three model predictions show the largest
%difference in $\langle\mu_{870}\rangle$.  The steep rise in the running
%average in this area is best reproduced by the model with the steep broken
%power-law luminosity function.  
Both models predict higher $\langle\mu_{870}\rangle$ than are seen in the data
by factors of 5-10.  However, the dispersion in the predicted
$\langle\mu_{870}\rangle$ values for both intrinsic luminosity functions rises
smoothly from $\sigma_\mu \approx 2$ at $S_{870} = 15\,$mJy to $\sigma_\mu
\approx 8$ at $S_{870} = 100\,$mJy, so this difference is not statistically
significant.  Furthermore, there is reason to believe that the data may be
biased against high magnification factor measurements.  In both the {\it
Herschel}-ALMA and {\it Herschel}-SMA samples, the spatial resolution is
$\approx 0\farcs5$.  This is nearly always sufficient to resolve the images of
the lensed galaxy, but it is not always sufficient to resolve the images
themselves.  Therefore, it may be the case that the lens models over-predict
the intrinsic sizes of the lensed galaxies and hence under-predict the
magnification factors.  For example, the half-light sizes of unlensed DSFGs
have been found recently to be $\approx 0.8 \,$kpc \citep{Ikarashi:2014nr} and
$\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  Early lens models
from higher resolution data with ALMA suggest that magnification factors could
increase by a factor of $\approx 1.5$ \citep{Rybak:2015fk}.  Therefore, it is
plausible that both of the intrinsic luminosity functions tested here provide
statistically consistent fits to the data.

@@

In the low flux density regime ($S_{870} < 10\,$mJy), each model predicts that
10\% of sources experience a magnification satisfying $\mu_{870} > 1.1$.  This
is in disagreement with the data, which show that $\sim 30\%$ of sources in
this flux density regime experience $\mu_{870} > 1.1$.  The cause of this
discrepancy is unclear.  One possibility is simply that we are dealing with
small number statistics.  We speculate that an alternative explanation might be
related to the excess number of sources $dN/dA$ found in our ALMA maps with
small separations from each other (reported in Section~\ref{sec:spatialdist}).
Essentially, if the {\it Herschel} sources have a high multiplicity rate, with
ALMA counterparts located close to each other, then adding a lens in front of
the {\it Herschel} source will magnify {\it all} of the ALMA counterparts.  If,
on the other hand, the ALMA counterparts were located far away from each other,
then adding a lens in front of the {\it Herschel} source would not necessarily
cause all ALMA counterparts to be magnified significantly.  For this reason, it
is plausible that the observed values reported in this figure are biased
upwards relative to the simulations outlined in Section~\ref{sec:statpredict}.

In the high flux density regime ($S_{870} > 10\,$mJy), all
three models as well as the running average in the data show a sharp transition
from low probability to high probability of being lensed (for either $\mu_{\rm
min} = 1.1$ or $\mu_{\rm min} = 2.0$).  However, there are major differences in
where this transition occurs.  For example, the steep Schechter function
predicts that 50\% of sources with $S_{870} = 50\,$mJy have $\mu_{870} < 1.1$.
This is inconsistent with the data, which show that all sources with $S_{870} >
50\,$mJy have $\mu_{870} > 1.1$.  The discrepancy is similar, albeit less
severe, for the luminosity function from \citet{Karim:2013lr}, where 50\% of
$S_{870} = 28\,$mJy sources are unlensed.  In contrast, the very steep broken
power-law luminosity function yields a model in which 50\% of sources with
$S_{870} = 10\,$mJy experience $\mu_{870} > 1.1$.  This is reasonably
consistent with the running average from the data.  These results are
qualitatively similar if the magnification threshold is increased from
$\mu_{\rm min} = 1.1$ to $\mu_{\rm min} = 2.0$.

If the steep power-law luminosity function is correct, the implications are
significant.  We should then expect to find $\approx 1$ source satisfying
$S_{870} > 10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 3
lower than the best-fit model in \citet{Karim:2013lr} and a factor of 7 lower
than our steep Schechter function.  Moreover, it is a factor of 20 lower than
typical measurements from single-dish, broad-beam studies
\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such as
GN20 and HFLS3 may be much more rare than previously thought.

@@

    \item 20/29 {\it Herschel} DSFGs break down into multiple ALMA
        counterparts.  Of the 9 isolated systems, 5 are strongly lensed by
        factors of 5-10.  After correcting for amplification, the brightest
        source in the sample has $S_{870} = 17.5 \pm 0.4\,$mJy.  There
        is a weak trend towards even higher multiplicity at the highest total
        $S_{870}$ flux densities.

    \item When a {\it Herschel} source comprises multiple ALMA counterparts,
        these counterparts are typically located within 2$\arcsec$ of each
        other.  Their separations are much smaller than ALMA counterparts to
        ALESS sources as well as simulated sources from \citet{HB13}.  This
        conclusion remains true even when we degrade our ALMA observations to
        match the spatial resolution, sensitivity, and {\it uv} coverage of the
        ALESS observations.

    \item Model predictions for the range of magnifications experienced by
        DSFGs in our sample indicate that a single Schechter function
        under-predicts the number of lensed sources with apparent $S_{870} >
        10\,$mJy.  Intrinsic luminosity functions with a broken power-law and a
        very steep decrease above 8$\,$mJy make better predictions for the
        fraction of lensed sources with $S_{870} > 10\,$mJy, but they also
        predict somewhat higher average magnification factors than are seen in
        combined sample of ALMA and SMA lens models.  This latter result could
        be explained by limitations in the spatial resolution of the ALMA and
        SMA imaging, which might lead to the lens models underestimating the
        magnification factors.

@@

Our findings suggest that galaxies with intrinsic flux densities above
$S_{870}^\prime \approx 10\,$mJy are extremely rare.  One possible explanation
for their rarity is that they are simply the tip of the mass function among
starbursts.  An alternative is that they represent a very short phase in galaxy
evolution.  Consistent with this idea is the high multiplicity rate in our ALMA
sample as well as the small projected separations between multiple ALMA
counterparts.  The inability of numerical simulations to reproduce the small
projected separations seen in the data might reflect an incomplete theoretical
understanding of the enhancement in star-formation by interactions and mergers
of galaxies which are already forming stars at a very high rate.

@@

\section{{\it Herschel}/SPIRE Photometry}

>>>>

The sample was selected to be the 29 brightest DSFGs in the Southern sky that
are not known radio AGN, nearby late-type galaxies, or Galactic emission. The
selection was designed to assemble a large sample of lensed galaxies in the
ALMA-accesible HerMES fields, and was constructed from the SUSSEXtractor
catalogs, which were available prior to the ALMA Cycle~0 deadline.
Subsequently, improved efforts to deblend SPIRE photometry at 500$\,\mu$m using
StarFinder \citep{Wang:2014lr} were introduced that formed the basis of the
lens selection criteria used in \citet{Wardlow:2013lr}.  As a result of the
improved deblending algorithms in the StarFinder catalogues and
\citet{Wardlow:2013lr} a number of objects in our sample have significantly
lower $S_{500}$ values in the StarFinder catalog than in the original
SUSSEXtractor catalogs.  This and further investigation into the StarFinder
catalogs shows that their original flux was boosted by blending with nearby
sources rather than by gravitational lensing.  For this reason, the objects in
this sample comprise a combination of lenses and blends of multiple sources.

We used positional priors based on the ALMA data presented in this paper to
obtain the best possible estimates of the total SPIRE flux densities for each
{\it Herschel} source.  We also used {\it Spitzer}/MIPS
\citep{2004ApJS..154...25R} imaging to take into consideration the presence of
nearby 24$\,\mu$m sources that are not detected by ALMA but may still
contribute to the 250$\,\mu$m emission detected by {\it Herschel}.  Additional
details on our methodology are provided in Section~\ref{sec:photometry}.  The
SPIRE flux densities measured in this way represent our ``fiducial'' flux
densities and are presented in Table~\ref{tab:positions}.  Interested readers
may refer to Table~\ref{tab:photometry} for a comparison of the fiducial,
StarFinder and SUSSEXtractor flux densities in tabular form.

@@

Figure~\ref{fig:sample} shows that the {\it Herschel}-ALMA sample is set
clearly apart from the very bright {\it Herschel} DSFGs that are selected to
have $S_{500} > 100 \, $mJy and have been shown to be almost entirely lensed
DSFGs \citep{Negrello:2010fk, Wardlow:2013lr, Bussmann:2013lr}.  In contrast,
the sample in this paper is expected to include a mix of lensed and unlensed
DSFGs.  On the other hand, the HerMES survey area is 200 times larger than that
of the Large Apex Bolometer Camera Extended Chandra Deep Field Survey
\citep[LESS][]{Weis:2009ly}.  This explains why the median $S_{500}$ in our
sample is $\sim4$ times brighter than the median $S_{500}$ in the sample of
ALMA-detected sources in LESS, known as ALESS \citep{Hodge:2013qy}.  Our {\it
Herschel}-ALMA sample opens a new window of discovery space on the bright end
of the DSFG luminosity function.

@@

Our methodology follows the procedures outlined in previous efforts to predict
magnification factors for DSFGs with a given apparent flux density
\citep[chiefly,][]{Lima:2010fk, Wardlow:2013lr, Fialkov:2015eu}.  We summarize
the essential elements here and highlight significant differences where
appropriate.

@@

To describe $\rho_{\rm lens}\,(r)$, we use a superposition of a singular
isothermal sphere (SIS) and a Navarro-Frenk-White (NFW) profile
\citep{Navarro:1997ys} that is truncated at the virial radius.  The NFW profile
describes the outskirts of dark matter halos better, while the SIS profile is
preferred on smaller scales because it correctly fits the observed flat
rotational curves in galaxies.  We make sure that the resulting probability
density of lensing, $P\,(\mu)$, is normalized to unity.  To describe $n_{\rm
lens}\,(M, \, z)$, we generate the abundance of halos at each mass and redshift
using the \citet{Sheth:1999kx} formalism.  To describe $dN_{\rm source}/dz$, we
adopt the following redshift distribution which is based on photometric
redshifts of optical counterparts to ALMA sources identified in ALESS
\citep{Simpson:2014lr}:

@@

\noindent where $a_z = 1 + z$, $z_\mu = 1.5$ (to reflect the relatively blue
SPIRE colors of the sample), and $\sigma_z = 0.2$.  Alternative
values for $z_\mu$ and $\sigma_z$ yield second-order perturbations which are
not significant at the level of our current analysis.

We explore two intrinsic luminosity functions that are intended to bracket the
plausible range of values for DSFGs based on two interferometric surveys.  One
is the luminosity function measured in ALESS \citep{Karim:2013lr}, and the
other is from interferometric follow-up of the first AzTEC survey in COSMOS
\citep{Scott:2008qy} using the SMA \citep{Younger:2007fk, Younger:2009lr} and
PdBI \citep{Miettinen:2015lr}.  These interferometric observations have shown
show that all of the sources in their surveys are either unlensed or lensed by
magnification factors $<2$.  This is why the ALESS and COSMOS luminosity
functions represent a plausible range of intrinsic luminosity functions for
DSFGs.  These luminosity functions are shown in the left panel of
Figure~\ref{fig:lensstats}.  Interferometric follow-up data in COSMOS
\citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are published, but
unknown completeness corrections in the single-dish surveys on which these
follow-up datasets are based precludes their use here.

In detail, we use a broken power-law of the form

@@

Table~\ref{tab:models} provides values for the parameters of the broken
power-law for the ALESS and COSMOS luminosity functions.  The data and
corresponding luminosity functions are shown in the left panel of
Figure~\ref{fig:lensstats}.

@@

The product of the model is the lensing optical depth for a given lensing
galaxy and source galaxy,  $f_\mu$. The lensing probability with magnification
larger than $\mu$ is then calculated via $P(>\mu) = 1-\exp(-f_\mu)$ and the
differential probability distribution is $P(\mu) = -dP(>\mu)/d\mu$.  The sum
over the distribution of source redshifts and lens masses and redshifts yields
the total probability distribution function.

The fundamental measurement provided by the spatially resolved SMA and ALMA
imaging and associated lens models is the magnification factor of a source with
a given apparent $S_{870}$.  We use the combined sample to compute the average
magnification as a function of $S_{870}$ from the data:
$\langle\mu_{870}\rangle$.  The same quantity can also be directly computed
from our model as

@@

%The regime between the low and high apparent flux density limits ($10\,$mJy$ <
%S_{870} < 70\,$mJy) is where the three model predictions show the largest
%difference in $\langle\mu_{870}\rangle$.  The steep rise in the running
%average in this area is best reproduced by the model with the steep broken
%power-law luminosity function.  
Both models predict higher $\langle\mu_{870}\rangle$ than are seen in the data
by factors of 5-10.  However, the dispersion in the predicted
$\langle\mu_{870}\rangle$ values for both intrinsic luminosity functions rises
smoothly from $\sigma_\mu \approx 2$ at $S_{870} = 15\,$mJy to $\sigma_\mu
\approx 8$ at $S_{870} = 100\,$mJy, so this difference is not statistically
significant.  Furthermore, there is reason to believe that the data may be
biased against high magnification factor measurements.  In both the {\it
Herschel}-ALMA and {\it Herschel}-SMA samples, the spatial resolution is
$\approx 0\farcs5$.  This is nearly always sufficient to resolve the images of
the lensed galaxy, but it is not always sufficient to resolve the images
themselves.  Therefore, it may be the case that the lens models over-predict
the intrinsic sizes of the lensed galaxies and hence under-predict the
magnification factors.  For example, the half-light sizes of unlensed DSFGs
have been found recently to be $\approx 0.8 \,$kpc \citep{Ikarashi:2014nr} and
$\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  Lens models from
higher resolution data with ALMA suggest that magnification factors could
increase by a factor of $\approx 1.5-2$ \citep{Rybak:2015fk, Tamura:2015lq,
Dye:2015fp}.  Therefore, it is plausible that both of the intrinsic luminosity
functions tested here provide statistically consistent fits to the data.

@@

%In the low flux density regime ($S_{870} < 10\,$mJy), each model predicts that
%10\% of sources experience a magnification satisfying $\mu_{870} > 1.1$.  This
%is in disagreement with the data, which show that $\sim 30\%$ of sources in
%this flux density regime experience $\mu_{870} > 1.1$.  The cause of this
%discrepancy is unclear.  One possibility is simply that we are dealing with
%small number statistics.  We speculate that an alternative explanation might be
%related to the excess number of sources $dN/dA$ found in our ALMA maps with
%small separations from each other (reported in Section~\ref{sec:spatialdist}).
%Essentially, if the {\it Herschel} sources have a high multiplicity rate, with
%ALMA counterparts located close to each other, then adding a lens in front of
%the {\it Herschel} source will magnify {\it all} of the ALMA counterparts.  If,
%on the other hand, the ALMA counterparts were located far away from each other,
%then adding a lens in front of the {\it Herschel} source would not necessarily
%cause all ALMA counterparts to be magnified significantly.  For this reason, it
%is plausible that the observed values reported in this figure are biased
%upwards relative to the simulations outlined in Section~\ref{sec:statpredict}.

Both models tested in this paper exhibit a sharp transition from low
probability to high probability of being lensed, consistent with the data.
However, there are significant differences in where this transition flux
density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
the data, the logistic regression fit yields $S_{\rm trans} = 24\,$mJy,
whereas the models based on the ALESS and COSMOS luminosity functions yield
$S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.

Note caveats.

This analysis highlights the difficulty encountered with the luminosity
function based on the COSMOS data: unlensed sources with $S_{870} > 50\,$mJy
are over-predicted and lensed sources with $S_{870} < 50\,$mJy are
under-predicted.  If the ALESS luminosity function continues to be supported by
the evidence as additional data are obtained, the implications are significant.
We should then expect to find $\approx 3$ sources satisfying $S_{870} >
10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 7 lower than
typical measurements from single-dish, broad-beam studies
\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such
as GN20 and HFLS3 may be much more rare than previously thought.

@@

    \item 20/29 {\it Herschel} DSFGs break down into multiple ALMA
        counterparts.  Of the 9 isolated systems, 5 are strongly lensed by
        factors of 5-10 (HECDFS12 is a non-isolated system with a strongly
        lensed source in it).  After correcting for amplification, the brightest
        source in the sample has $S_{870} = 17.5 \pm 0.4\,$mJy.  There
        is a weak trend towards even higher multiplicity at the highest total
        $S_{870}$ flux densities.

    \item When a {\it Herschel} source comprises multiple ALMA counterparts,
        these counterparts are typically located within 2$\arcsec$ of each
        other.  Their separations are significantly smaller than ALMA
        counterparts to ALESS sources as well as simulated sources from
        \citet{HB13}.  This conclusion remains true even when we degrade our
        ALMA observations to match the spatial resolution, sensitivity, and
        {\it uv} coverage of the ALESS observations.

    \item An intrinsic luminosity function for DSFGs with a form that matches
        observations in COSMOS \citep{Miettinen:2015lr} under-predicts the
        number of lensed sources with apparent $S_{870} > 10\,$mJy.  A
        luminosity function based on ALESS observations provides a better match
        to our magnification measurements.  The interpretation of these results
        is complicated by the fact that our sample is likely biased towards
        blends of multiple sources within a {\it Herschel} beam.  Our primary
        goal is to draw attention to this analysis method as a means to test
        luminosity functions of DSFGs using wide-field {\it Herschel} data.

@@

If the ALESS luminosity function continues to provide the best predicted
magnification factors in larger samples with weaker biases, this suggests that
galaxies with intrinsic flux densities above $S_{870}^\prime \approx 10\,$mJy
are extremely rare.  One possible explanation for their rarity is that they are
simply the tip of the mass function among starbursts.  An alternative is that
they represent a very short phase in galaxy evolution.  It is interesting to
note that consistent with this idea is the high multiplicity rate in our ALMA
sample as well as the small projected separations between multiple ALMA
counterparts.  The inability of numerical simulations to reproduce the small
projected separations seen in the data might highlight a productive path
forward to improve our theoretical understanding of the enhancement in
star-formation by interactions and mergers of galaxies which are already
forming stars at a very high rate.

@@

\section{{\it Herschel}/SPIRE Photometry}\label{sec:photometry}
